\documentclass{resume} % Use the custom resume.cls style
\usepackage{ragged2e}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Archit Srivastava} % Your name
% You can merge both of these into a single line, if you do not have a website.
%\address{+1(123) 456-7890 \\ San Francisco, CA} 
\address{\href{mailto:architsrivastava3115@gmail.com}{architsrivastava3115@gmail.com} \\ \href{https://www.linkedin.com/in/architsrivastava3115/}{Linkedin} \\ \href{https://github.com/Archit3115}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{ABOUT}

{At my core, I am a progressive and empathetic leader capable of completing the seemingly impossible tasks in most adverse situations with absolute calm and composure. The challenges of new developing technologies in the frontiers of science has always intrigue and fueled my research capabilities. I always look for opportunities that help me increase my domain knowledge, which eventually will help me to develop efficient and effective solutions to make this world, a better place to live.}


\end{rSection}

\begin{rSection}{INTERNSHIPS \& EXPERIENCES}

\textbf{Data Analyst - BI Developer} \hfill Feb 2021 - Present\\
Hewlett Packard Enterprise \hfill \textit{Bengaluru, Karnataka, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Working in the Global Fulfillment Analytic Team of Supply Chain Management as a \textbf{BI Developer}.
     \item Automated a manual report and reduced the manual effort by \textbf{90\%} with a \textbf{World Wide Scope}. 
     
    \item Connection and automation of remote database to frontend dashboard is done via \textbf{SSIS} Packages.
    \item Briefly learned about big data tools like \textbf{HIVE}, \textbf{Hadoop} and \textbf{PIG} with developments on the basics of Big Data
    
 
 \end{itemize}
 
\textbf{Senior Research Associate} \hfill Aug 2020 - Present\\
Quantum Computing India \hfill \textit{Bengaluru, Karnataka, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item  Worked in the domains like \textbf{Quantum Cryptography} \& \textbf{Quantum Hardware}, and helped to develop them.
     \item Researched about different \textbf{QKD} Schemes like \textbf{BB84 \& B92} and their practical use case analysis in drones.
     \item Worked on knowledge development about \textbf{Quantum Hardware} and researched about various architectures.
     \item Researched about \textbf{continuous variable} quantum computing and application of the same in Cryptography.
     %\item Led XYZ which led to X\% of improvement in ABC
    %\item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\end{rSection} 
%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & A, B, C, D
\\
Soft Skills & A, B, C, D\\
XYZ & A, B, C, D\\
\end{tabular}\\

\end{rSection}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Sample section
\end{itemize}


\end{rSection}

%-------------------------------------------------
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%{\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
%Relevant Coursework: A, B, C, and D.

{\bf B.E - Electronics \& Instrumentation Engineering}  \hfill {2017 - 2021} \\
\textit{RV College of Engineering} \hfill {Bengaluru, Karnataka, India}\\
\textit{CGPA - \textbf{7.16}}

{\bf All India Secondary School Certificate Exam - Class XII} \hfill{2017} \\ \textit{Delhi Public School} \hfill{Bokaro Steel City, Jharkhand, India} \\ 
\textit{Score - \textbf{91.4\%}}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\end{document}
